Preregistered as Code: Gender differences in Machiavellianism

### 2021-07-27 preregistration.Rmd
add full stop and linebreaks

Machiavellianism describes a personality dimension characterized by a cynical disregard of morals in the pursuit of one's own interest, e.g. through manipulation [@christie1970].
There is extensive literature reporting differences in the dark triad (narcissism, machiavellianism, and psychopathy) between self-identified males and females [@muris2017] but only few studies focus solely on machiavellianism
We aim to replicate the finding that males tend to have higher machiavellianism scores [@muris2017].
<!--end-theory-->
This research question serves as a testbed for preregistration as code (PAC) to examine if PAC is feasible under realistic conditions.
In the PAC paradigm, all analysis code is written before real data are gathered or accessed the first time.

>>>>

Machiavellianism describes a personality dimension characterized by a cynical disregard of morals in the pursuit of one's own interest, e.g. through manipulation [@christie1970].
There is extensive literature reporting differences in the dark triad (narcissism, machiavellianism, and psychopathy) between self-identified males and females [@muris2017] but only few studies focus solely on machiavellianism.
We aim to replicate the finding that males tend to have higher machiavellianism scores [@muris2017].
<!--end-theory-->
This research question serves as a testbed for preregistration as code (PAC) to examine if PAC is feasible under realistic conditions.
In the PAC paradigm, all analysis code is written before real data are gathered or accessed the first time.
